\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape First Last} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:email@address.com}{\underline{email@address.com}} $|$ 
    \href{https://linkedin.com/in/username}{\underline{linkedin.com/in/username}} $|$
    \href{https://github.com/username}{\underline{github.com/username}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Name}{City, State}
      {Bachelor of Science in Computer Science}{Month Year -- Month Year}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Company Name}{City, State}
      {Software Engineer}{Month Year -- Present}
      \resumeItemListStart
        \resumeItem{Developed and maintained scalable web applications using React and Node.js, improving system performance by 25\%.}
        \resumeItem{Designed and implemented a RESTful API that handled over 10,000 concurrent requests per minute with 99.9\% uptime.}
        \resumeItem{Collaborated with cross-functional teams to integrate AWS cloud services, reducing infrastructure costs by 15\%.}
        \resumeItem{Automated CI/CD pipelines using Jenkins and Docker, decreasing deployment time from 1 hour to 10 minutes.}
      \resumeItemListEnd

    \resumeSubheading
      {Company Name}{City, State}
      {Junior Developer}{Month Year -- Month Year}
      \resumeItemListStart
        \resumeItem{Optimized SQL database queries, resulting in a 40\% reduction in average page load times for the client dashboard.}
        \resumeItem{Refactored legacy codebase to modern standards, increasing code coverage from 60\% to 85\% via unit and integration tests.}
        \resumeItem{Resolved over 150 critical bugs reported in the production environment within a 6-month period.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Project Name} $|$ \emph{Python, Flask, PostgreSQL, React}}{Month Year}
          \resumeItemListStart
            \resumeItem{Built a full-stack e-commerce platform featuring secure user authentication and Stripe payment integration.}
            \resumeItem{Implemented a real-time inventory tracking system using WebSockets to synchronize data across multiple users.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Portfolio Website} $|$ \emph{HTML/CSS, JavaScript, GitHub Actions}}{Month Year}
          \resumeItemListStart
            \resumeItem{Designed a responsive personal portfolio site to showcase projects, achieving an 80+ accessibility score on Lighthouse.}
            \resumeItem{Configured automated deployment workflows using GitHub Actions for seamless updates.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, Flask, Spring Boot, JUnit, Material-UI} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Jenkins, Postman, Kubernetes} \\
     \textbf{Libraries}{: NumPy, Pandas, Scikit-Learn, Redux}
    }}
 \end{itemize}

\end{document}